Secondary analyses

### 2025-06-23 analysis/primary_analyses.qmd
format tables

```{r}
dat_desc <- bind_rows(
  dat_poly |> select(Geschlecht, Bildung, Muttersprache, Alter_realW) |> mutate(categories = "6 categories"),
  dat_dich |> select(Geschlecht, Bildung, Muttersprache, Alter_realW) |> mutate(categories = "2 categories")
)
# dat_desc |> group_by(categories, Geschlecht) |>
#   summarize(N = n()) |> mutate(perc = N / sum(N))
# dat_desc |> group_by(categories, Bildung) |>
#   summarize(N = n()) |> mutate(perc = N / sum(N))
# dat_desc |> group_by(categories, Muttersprache) |>
#   summarize(N = n()) |> mutate(perc = N / sum(N))
# dat_desc |> group_by(categories) |>
#   summarize(MD = median(Alter_realW), SD = sd(Alter_realW), N = n())

table1 <- dat_desc |>
  rename(Gender = Geschlecht, Education = Bildung, `Mother tongue` = Muttersprache, Age = Alter_realW) |>
  mutate(Gender = factor(Gender, levels = 1:2, labels = c("women", "men")), 
    Education = factor(Education, levels = 1:6, labels = c("no school leaving certificate", "secondary school leaving certificate/elementary school or equivalent", "secondary school or equivalent", "vocational baccalaureate or high school diploma", "college degree or university degree", "doctorate or habilitation")), 
    `Mother tongue` = factor(`Mother tongue`, levels = 1:2, labels = c("German", "Other"))) |>
  flextable::summarizor(by = "categories") |>
  flextable::as_flextable() |>
  flextable::theme_apa() |>
  ftExtra::colformat_md()
table1
```

@@

table2 <- rbind(
    load_df_nomod_proc |> rename(Measure = item) |> mutate(group = "Items"),
    fit_df |> rename(Measure = statistic) |> mutate(group = "Fit")
  ) |> 
  group_by(group) |>
  flextable::as_grouped_data(groups = "group") |>
  flextable::as_flextable(hide_grouplabel = TRUE) |>
  flextable::add_header_row(values = c("Measure", "Age", "Height", "Weight"),
    colwidths = c(1, 2, 2, 2)) |>
  flextable::set_header_labels(
    values = list(
      Measure = "Categories",
      age_6 = "6", age_2 = "2", 
      height_6 = "6", height_2 = "2",
      weight_6 = "6", weight_2 = "2")) |>
  flextable::align(i = 1, align = "center", part = "header") |>
  flextable::border(i = 2, j = 1, border.top = officer::fp_border(width = 0), part = "header") |>
  flextable::border(i = 1, j = 1, border.bottom = officer::fp_border(width = 0), part = "header") |>
  flextable::theme_apa() |>
  ftExtra::colformat_md()
table2
```

@@

load_df_bifac_proc <- load_df_bifac |>
  mutate(
    cause = case_when(
      lhs %in% c("age", "height", "weight") & op == "=~" ~ lhs,
      rhs %in% c("Alter_realW", "Koerpergroesse_realW", "Koerpergewicht_realW", "Geschlecht") & op == "~" ~ rhs),
    item_name = case_when(
      lhs %in% c("age", "height", "weight") & op == "=~" ~ rhs,
      rhs %in% c("Alter_realW", "Koerpergroesse_realW", "Koerpergewicht_realW", "Geschlecht") & op == "~" ~ lhs
    )) |> 
  # Create new columns: prefix (everything before underscore) and suffix (the numeric part)
  mutate(prefix = sub("_.*", "", item_name),
    suffix = as.numeric(sub(".*_", "", item_name))) |>
  # For each prefix group, assign new_num as the rank of suffix in sorted order 
  group_by(prefix) |>
  mutate(item = match(suffix, sort(unique(suffix)))) |>
  ungroup() |>
  mutate(est_print = papaja::printnum(est.std, gt1 = FALSE, digits = 3))
```

```{r}
table3 <- load_df_bifac_proc |> 
  select(item, cause, measure, categories, est_print) |> 
  pivot_wider(names_from = c(measure, cause), values_from = est_print) |>
  flextable::as_grouped_data(groups = "categories") |>
  flextable::as_flextable(hide_grouplabel = TRUE) |>
  flextable::add_header_row(values = c("age", "height", "weight"),
    colwidths = c(4, 3, 3)) |>
  flextable::set_header_labels(
    values = list(
      item = "Item",
      age_age = "LV", height_height = "LV", weight_weight = "LV",
      age_Alter_realW = "age",
      height_Koerpergroesse_realW = "height",
      weight_Koerpergewicht_realW = "weight",
      age_Geschlecht = "sex", height_Geschlecht = "sex", weight_Geschlecht = "sex")) |>
  flextable::align(i = 1, align = "center", part = "header") |>
  flextable::border(i = 2, j = 1, border.top = officer::fp_border(width = 0), part = "header") |>
  flextable::border(i = 1, j = 1, border.bottom = officer::fp_border(width = 0), part = "header") |>
  flextable::theme_apa() |>
  ftExtra::colformat_md()
table3
```

@@

```{r}
(r_latent_poly <- standardizedSolution(fit1ges6, type = "std.all") |>
  filter(op == "~~" & 
      lhs %in% c("age", "height", "weight") &
      rhs %in% c("age", "height", "weight") &
      lhs != rhs) |>
  mutate(est_print = papaja::printnum(est.std, gt1 = FALSE, digits = 3))) |>
  mutate(est_print = case_when(
    pvalue < 0.05 & pvalue > 0.01 ~ paste0(est_print, "*"),
    pvalue < 0.01 & pvalue > 0.001 ~ paste0(est_print, "**"),
    pvalue < 0.01 ~ paste0(est_print, "***"),
    .default = est_print 
  ))
r_latent_AG6 <- r_latent_poly |> filter(lhs == "age" & rhs == "height") |> pull(est_print)
r_latent_AGe6 <- r_latent_poly |> filter(lhs == "age" & rhs == "weight") |> pull(est_print)
r_latent_GGe6 <- r_latent_poly |> filter(lhs == "height" & rhs == "weight") |> pull(est_print)

(r_latent_dich <- standardizedSolution(fit1ges2, type = "std.all") |>
  filter(op == "~~" & 
      lhs %in% c("age", "height", "weight") &
      rhs %in% c("age", "height", "weight") &
      lhs != rhs) |>
  mutate(est_print = papaja::printnum(est.std, gt1 = FALSE, digits = 3))) |>
  mutate(est_print = case_when(
    pvalue < 0.05 & pvalue > 0.01 ~ paste0(est_print, "*"),
    pvalue < 0.01 & pvalue > 0.001 ~ paste0(est_print, "**"),
    pvalue < 0.01 ~ paste0(est_print, "***"),
    .default = est_print 
  ))
r_latent_AG2 <- r_latent_dich |> filter(lhs == "age" & rhs == "height") |> pull(est_print)
r_latent_AGe2 <- r_latent_dich |> filter(lhs == "age" & rhs == "weight") |> pull(est_print)
r_latent_GGe2 <- r_latent_dich |> filter(lhs == "height" & rhs == "weight") |> pull(est_print)
```

@@

```{r}
(r_real_poly <- corx(data = dat_poly |>
    select(Alter_realW, Koerpergroesse_realW, Koerpergewicht_realW),
  method = "pearson"))

@@

(r_real_dich <- corx(data = dat_dich |>
    select(Alter_realW, Koerpergroesse_realW, Koerpergewicht_realW),
  method = "pearson"))

@@

```{r}
cor_table <- tribble(
  ~Measure, ~Age_6     , ~Age_2     , ~Height_6   , ~Height_2   , ~Weight_6    , ~Weight_2    ,
  "Age"   , rel_A6     , rel_A2     , r_latent_AG6, r_latent_AG2, r_latent_AGe6, r_latent_AGe2,
  "Height", r_real_AG6 , r_real_AG2 , rel_G6      , rel_G2      , r_latent_GGe6, r_latent_GGe2,
  "Weight", r_real_AGe6, r_real_AGe2, r_real_GGe6 , r_real_GGe2 , rel_Ge6      , rel_Ge2      
)
```

```{r}
table4 <- flextable::flextable(cor_table) |>
  flextable::set_header_labels(
    Measure = "Categories",
    Age_6 = "6", Age_2 = "2",
    Height_6 = 6, Height_2 = 2,
    Weight_6 = 6, Weight_2 = 2) |>
  flextable::add_header_row(values = c("Measure", "Age", "Height", "Weight"),
    colwidths = c(1, 2, 2, 2)) |>
  flextable::align(i = 1, align = "center", part = "header") |>
  flextable::border(i = 2, j = 1, border.top = officer::fp_border(width = 0), part = "header") |>
  flextable::border(i = 1, j = 1, border.bottom = officer::fp_border(width = 0), part = "header") |>
  flextable::theme_apa() |>
  ftExtra::colformat_md()
table4
```

>>>>

```{r}
dat_desc <- bind_rows(
  dat_poly |> select(Alter_realW, Geschlecht, Bildung, Muttersprache) |> mutate(categories = "6"),
  dat_dich |> select(Alter_realW, Geschlecht,Bildung, Muttersprache) |> mutate(categories = "2")
)

table1 <- dat_desc |>
  rename(Gender = Geschlecht, Education = Bildung, `Mother tongue` = Muttersprache, Age = Alter_realW) |>
  mutate(categories = factor(categories, levels = c(2, 6), labels = c("Two categories", "Six categories")),
    Gender = factor(Gender, levels = 1:2, labels = c("Women", "Men")), 
    Education = factor(Education, levels = 1:6, labels = c("No school leaving certificate", "Secondary school leaving certificate/elementary school or equivalent", "Secondary school or equivalent", "Vocational baccalaureate or high school diploma", "College degree or university degree", "Doctorate or habilitation")), 
    `Mother tongue` = factor(`Mother tongue`, levels = 1:2, labels = c("German", "Other"))) |>
  flextable::summarizor(by = "categories") |>
  flextable::as_flextable() |>
  flextable::theme_apa() |>
  ftExtra::colformat_md()
table1
```

@@

table2 <- rbind(
    load_df_nomod_proc |> select(item, height_2, height_6, weight_2, weight_6, age_2, age_6) |> rename(Measure = item) |> mutate(group = "Items"),
    fit_df |> select(statistic, height_2, height_6, weight_2, weight_6, age_2, age_6) |> rename(Measure = statistic) |> mutate(group = "Model fit")
  ) |> 
  group_by(group) |>
  flextable::as_grouped_data(groups = "group") |>
  flextable::as_flextable(hide_grouplabel = TRUE) |>
  flextable::add_header_row(values = c("Measure", "Height", "Weight", "Age"),
    colwidths = c(1, 2, 2, 2)) |>
  flextable::set_header_labels(
    values = list(
      Measure = "Categories",
      age_6 = "Six", age_2 = "Two", 
      height_6 = "Six", height_2 = "Two",
      weight_6 = "Six", weight_2 = "Two")) |>
  flextable::align(i = 1, align = "center", part = "header") |>
  flextable::border(i = 2, j = 1, border.top = officer::fp_border(width = 0), part = "header") |>
  flextable::border(i = 1, j = 1, border.bottom = officer::fp_border(width = 0), part = "header") |>

  flextable::bold(i = ~ age_6 > age_6[14], j = "age_6") |>
  flextable::bold(i = ~ age_2 > age_2[14], j = "age_2") |>
  flextable::bold(i = ~ height_6 > height_6[14], j = "height_6") |>
  flextable::bold(i = ~ height_2 > height_2[14], j = "height_2") |>
  flextable::bold(i = ~ weight_6 > weight_6[14], j = "weight_6") |>
  flextable::bold(i = ~ weight_2 > weight_2[14], j = "weight_2") |>
  flextable::bold(i = 15:21, bold = FALSE) |>
  flextable::bg(i  = 14, bg = "grey90") |>

  flextable::theme_apa() |>
  ftExtra::colformat_md()
table2
```

@@

load_df_bifac_proc <- load_df_bifac |>
  mutate(
    cause = case_when(
      lhs %in% c("age", "height", "weight") & op == "=~" ~ lhs,
      rhs %in% c("Alter_realW", "Koerpergroesse_realW", "Koerpergewicht_realW", "Geschlecht") & op == "~" ~ rhs),
    item_name = case_when(
      lhs %in% c("age", "height", "weight") & op == "=~" ~ rhs,
      rhs %in% c("Alter_realW", "Koerpergroesse_realW", "Koerpergewicht_realW", "Geschlecht") & op == "~" ~ lhs
    )) |> 
  # Create new columns: prefix (everything before underscore) and suffix (the numeric part)
  mutate(prefix = sub("_.*", "", item_name),
    suffix = as.numeric(sub(".*_", "", item_name))) |>
  # For each prefix group, assign new_num as the rank of suffix in sorted order 
  group_by(prefix) |>
  mutate(item = match(suffix, sort(unique(suffix)))) |>
  ungroup() |>
  mutate(est_print = papaja::printnum(est.std, gt1 = TRUE, digits = 3))
```

```{r}
table3 <- load_df_bifac_proc |> 
  select(item, cause, measure, categories, est_print) |> 
  pivot_wider(names_from = c(measure, cause), values_from = est_print) |>
  select(item, categories, height_height, height_Koerpergroesse_realW, height_Geschlecht, weight_weight, weight_Koerpergewicht_realW, weight_Geschlecht, age_age, age_Alter_realW, age_Geschlecht) |>
  mutate(categories = factor(categories, levels = c(2, 6), labels = c("Two categories", "Six categories"))) |>
  arrange(categories, item) |>
  flextable::as_grouped_data(groups = "categories") |>
  flextable::as_flextable(hide_grouplabel = TRUE) |>
  flextable::add_header_row(values = c("", "Height", "Weight", "Age"),
    colwidths = c(1, 3, 3, 3)) |>
  flextable::set_header_labels(
    values = list(
      item = "Item",
      age_age = "Latent", height_height = "Latent", weight_weight = "Latent",
      age_Alter_realW = "Physical",
      height_Koerpergroesse_realW = "Physical",
      weight_Koerpergewicht_realW = "Physical",
      age_Geschlecht = "Gender", height_Geschlecht = "Gender", weight_Geschlecht = "Gender")) |>
  flextable::align(i = 1, align = "center", part = "header") |>
  flextable::border(i = 2, j = 1, border.top = officer::fp_border(width = 0), part = "header") |>
  flextable::border(i = 1, j = 1, border.bottom = officer::fp_border(width = 0), part = "header") |>

  flextable::bold(i = ~ age_age > 0.6, j = "age_age") |>
  flextable::bold(i = ~ age_Alter_realW > 0.6, j = "age_Alter_realW") |>
  flextable::bold(i = ~ age_Geschlecht > 0.6, j = "age_Geschlecht") |>
  flextable::bold(i = ~ height_height > 0.6, j = "height_height") |>
  flextable::bold(i = ~ height_Koerpergroesse_realW > 0.6, j = "height_Koerpergroesse_realW") |>
  flextable::bold(i = ~ height_Geschlecht > 0.6, j = "height_Geschlecht") |>
  flextable::bold(i = ~ weight_weight > 0.6, j = "weight_weight") |>
  flextable::bold(i = ~ weight_Koerpergewicht_realW > 0.6, j = "weight_Koerpergewicht_realW") |>
  flextable::bold(i = ~ weight_Geschlecht > 0.6, j = "weight_Geschlecht") |>

  flextable::theme_apa() |>
  ftExtra::colformat_md()
table3
```

@@

```{r}
(r_latent_poly <- standardizedSolution(fit1ges6, type = "std.all") |>
  filter(op == "~~" & 
      lhs %in% c("age", "height", "weight") &
      rhs %in% c("age", "height", "weight") &
      lhs != rhs) |>
  mutate(est_print = papaja::printnum(est.std, gt1 = FALSE, digits = 3)) |>
  mutate(est_print_star = case_when(
    pvalue < 0.05 & pvalue > 0.01 ~ paste0(est_print, "*"),
    pvalue < 0.01 & pvalue > 0.001 ~ paste0(est_print, "**"),
    pvalue < 0.001 ~ paste0(est_print, "***"),
    .default = est_print 
  )))
r_latent_AG6 <- r_latent_poly |> filter(lhs == "age" & rhs == "height") |> pull(est_print_star)
r_latent_AGe6 <- r_latent_poly |> filter(lhs == "age" & rhs == "weight") |> pull(est_print_star)
r_latent_GGe6 <- r_latent_poly |> filter(lhs == "height" & rhs == "weight") |> pull(est_print_star)

(r_latent_dich <- standardizedSolution(fit1ges2, type = "std.all") |>
  filter(op == "~~" & 
      lhs %in% c("age", "height", "weight") &
      rhs %in% c("age", "height", "weight") &
      lhs != rhs) |>
  mutate(est_print = papaja::printnum(est.std, gt1 = FALSE, digits = 3)) |>
  mutate(est_print_star = case_when(
    pvalue < 0.05 & pvalue > 0.01 ~ paste0(est_print, "*"),
    pvalue < 0.01 & pvalue > 0.001 ~ paste0(est_print, "**"),
    pvalue < 0.001 ~ paste0(est_print, "***"),
    .default = est_print 
  )))
r_latent_AG2 <- r_latent_dich |> filter(lhs == "age" & rhs == "height") |> pull(est_print_star)
r_latent_AGe2 <- r_latent_dich |> filter(lhs == "age" & rhs == "weight") |> pull(est_print_star)
r_latent_GGe2 <- r_latent_dich |> filter(lhs == "height" & rhs == "weight") |> pull(est_print_star)
```

@@

```{r}
(r_real_poly <- corx(data = dat_poly |>
    select(Alter_realW, Koerpergroesse_realW, Koerpergewicht_realW),
  method = "pearson", stars = c(0.05, 0.01, 0.001)))

@@

(r_real_dich <- corx(data = dat_dich |>
    select(Alter_realW, Koerpergroesse_realW, Koerpergewicht_realW),
  method = "pearson", stars = c(0.05, 0.01, 0.001)))

@@

```{r}
cor_table <- tribble(
  ~Measure, ~Height_2  , ~Height_6  , ~Weight_2    , ~Weight_6    , ~Age_2       , ~Age_6       ,
  "Height", rel_G2     , rel_G6     , r_latent_GGe2, r_latent_GGe6, r_latent_AG2 , r_latent_AG6 ,
  "Weight", r_real_GGe2, r_real_GGe6, rel_Ge2      , rel_Ge6      , r_latent_AGe2, r_latent_AGe6,
  "Age"   , r_real_AG2 , r_real_AG6 , r_real_AGe2  , r_real_AGe6  , rel_A2       , rel_A6      
)
```

```{r}
table4 <- flextable::flextable(cor_table) |>
  flextable::set_header_labels(
    Measure = "Categories",
    Age_6 = "Six", Age_2 = "Two",
    Height_6 = "Six", Height_2 = "Two",
    Weight_6 = "Six", Weight_2 = "Two") |>
  flextable::add_header_row(values = c("Measure", "Height", "Weight", "Age"),
    colwidths = c(1, 2, 2, 2)) |>
  flextable::align(i = 1, align = "center", part = "header") |>
  flextable::border(i = 2, j = 1, border.top = officer::fp_border(width = 0), part = "header") |>
  flextable::border(i = 1, j = 1, border.bottom = officer::fp_border(width = 0), part = "header") |>

  flextable::bold(i  = 1, j = 4:7) |>
  flextable::bold(i  = 2, j = 6:7) |>

  flextable::bg(i  = 1, j = c(2, 3), bg = "grey90") |>
  flextable::bg(i  = 2, j = c(4, 5), bg = "grey90") |>
  flextable::bg(i  = 3, j = c(6, 7), bg = "grey90") |>

  flextable::theme_apa() |>
  ftExtra::colformat_md()
table4
```

### 2025-06-23 analysis/secondary_analyses.qmd
format tables

table5 <- rbind(
    load_df_mod_proc |> rename(Measure = item) |> mutate(group = "Items"),
    fit_df |> rename(Measure = statistic) |> mutate(group = "Fit")
  ) |> 
  group_by(group) |>
  flextable::as_grouped_data(groups = "group") |>
  flextable::as_flextable(hide_grouplabel = TRUE) |>
  flextable::add_header_row(values = c("Measure", "Age", "Height", "Weight"),
    colwidths = c(1, 2, 2, 2)) |>
  flextable::set_header_labels(
    values = list(
      Measure = "Categories",
      age_6 = "6", age_2 = "2", 
      height_6 = "6", height_2 = "2",
      weight_6 = "6", weight_2 = "2")) |>
  flextable::align(i = 1, align = "center", part = "header") |>
  flextable::border(i = 2, j = 1, border.top = officer::fp_border(width = 0), part = "header") |>
  flextable::border(i = 1, j = 1, border.bottom = officer::fp_border(width = 0), part = "header") |>
  flextable::theme_apa() |>
  ftExtra::colformat_md()
table5
```

>>>>

table5 <- rbind(
    load_df_mod_proc |> select(item, height_2, height_6, weight_2, weight_6, age_2, age_6) |> rename(Measure = item) |> mutate(group = "Items"),
    fit_df |> select(statistic, height_2, height_6, weight_2, weight_6, age_2, age_6) |> rename(Measure = statistic) |> mutate(group = "Model fit")
  ) |> 
  group_by(group) |>
  flextable::as_grouped_data(groups = "group") |>
  flextable::as_flextable(hide_grouplabel = TRUE) |>
  flextable::add_header_row(values = c("Measure", "Height", "Weight", "Age"),
    colwidths = c(1, 2, 2, 2)) |>
  flextable::set_header_labels(
    values = list(
      Measure = "Categories",
      age_6 = "Six", age_2 = "Two", 
      height_6 = "Six", height_2 = "Two",
      weight_6 = "Six", weight_2 = "Two")) |>
  flextable::align(i = 1, align = "center", part = "header") |>
  flextable::border(i = 2, j = 1, border.top = officer::fp_border(width = 0), part = "header") |>
  flextable::border(i = 1, j = 1, border.bottom = officer::fp_border(width = 0), part = "header") |>

  flextable::bold(i = ~ age_6 > age_6[14], j = "age_6") |>
  flextable::bold(i = ~ age_2 > age_2[14], j = "age_2") |>
  flextable::bold(i = ~ height_6 > height_6[14], j = "height_6") |>
  flextable::bold(i = ~ height_2 > height_2[14], j = "height_2") |>
  flextable::bold(i = ~ weight_6 > weight_6[14], j = "weight_6") |>
  flextable::bold(i = ~ weight_2 > weight_2[14], j = "weight_2") |>
  flextable::bold(i = 15:21, bold = FALSE) |>
  flextable::bg(i  = 14, bg = "grey90") |>

  flextable::theme_apa() |>
  ftExtra::colformat_md()
table5
```
